---
title: "Diamonds"
author: "Willem Hogewoning"
date: "10-4-2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 2 - Diamonds

Date: 10-4-2021

### introduction
This presentation is part of : Peer-graded Assignment: Course Project: Shiny Application and Reproducible Pitch
Which containers out of 2 assignments:
- Create a Shinny App
- Create a Presentation


## 3 - Diamonds Selector

For the app I have used the diamonds dataset which is standard available when you load the ggplot package.
(or the tidyverse packets, which also loads the ggplot package ;-).

I have created a selector with works as a filter on the diamonds dataset.
This demontrates how you quickly can make a interactive filter, for anyone to use.

The app is at: https://willemhogewoning.shinyapps.io/shinny/

## 4 dataset
As shown here a small overview of the dataset.

```{r  echo = TRUE, size=12}
library(ggplot2)
summary(diamonds$carat)
summary(diamonds$price)
```

## 5 Dataset Histogram
Here is the dataset shown in a historgram


```{r }
hist(diamonds$price)
```
rsconnect::deployApp('path/to/your/app')

